%-------------------------
% Resume in Latex
% Author : Bhaskar Dixit
% License : DUD
%------------------------

\documentclass{resume}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Bhaskar Dixit} \\
    % \vspace{-9pt}
    % \begin{center} \textbf{ \large Full Stack Software Engineer}\end{center}
     % \vspace{10pt}
    % \vspace*{-16mm}

    \small
    \faMobile \hspace{.5pt} \href{tel:917030348751}{+91 7030348751}
    $|$
    \faAt \hspace{.5pt} \href{mailto:dixit.bhaskar@outlook.com}{dixit.bhaskar@outlook.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/bhaskar-dixit}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{https://github.com/devBhaskar98}{GitHub}
    % $|$
    % \faGlobe \hspace{.5pt} \href{https://arasgungore.github.io}{Portfolio}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://maps.app.goo.gl/cxQaZHjSpMqCGx5s9}{Mumbai, Maharashtra}
\end{center}

%----------- PROFILE -----------
\section{Profile}
{ Seasoned software engineer professional proficient in orchestrating the full lifecycle development of successful web applications. Demonstrated prowess in software design, implementation, and project management across various frameworks, tools, and programming languages, with a particular emphasis on Angular and Java technologies. }

%----------- EXPERIENCE -----------
\section{Professional Experience}
\vspace{3pt}

% COMPANY - Mobile Programming
    \resumeSubHeadingListStart
    \resumeSubheading
          {Mobile Programming LLC}{Pune, Maharashtra}
          {Software Engineer}{Oct 2021 \textbf{--} Present, Full-time}
    
    \resumeItemListStart
    % ######### PROJECT 3 #########
    \projectOneHead
    {Xcelerator Admin Console  (\normalfont \textit{for Siemens DISW})}{Oct 2021 -- Present}
        % Summary
        \begin
            {itemize}[leftmargin=0in, label={-}]
            \item\small It is a web application for customer adminstration to manage subscriptions of Cloud SaaS Products.
            \item\small Rebuild the project using Angular and Spring Boot, significantly improving performance and scalability.
            \item\small Apply agile methodologies to accelerate development and testing cycles for bug fixes.
            \item\small Oversee new product releases, coordinating development and QA testing, manage deployments to production with CI/CD pipelines, and showcase new features during sprint reviews.
            \item\small Architect a solution to serve Angular bundle files from CloudFront, handling requests via Kong Gateway on AWS.
            \item\small Implement security measures, including fixes, patches, and configuration changes, to effectively mitigate risks.
            \item\small Ensure code stability through comprehensive testing and quality assurance practices.
            \item\small Streamline deployment processes across Zeus projects by creating a unified GitLab YAML configuration, enhancing workflow consistency and team collaboration.
            
        \end{itemize}

        % Skills
        \begin{itemize}[leftmargin=-0.15in, label={}]
            \item\textit{\textbf{\fontsize{10}{12}\selectfont Java, Typescript, Spring Boot, Node JS, Angular, Web Application, Microservices, Docker, Kibana, Gitlab, Coverity, Sonar, AWS, VS, VS Code, Postman, Git, Jest, Junit}}
        \end{itemize}

    
    \resumeItemListEnd
    \resumeSubHeadingListEnd
    
% COMPANY - Paramatrix Technologies
    \resumeSubHeadingListStart
    \firstCompanyHeading
          {Paramatrix Technologies Pvt Ltd}{Mumbai, Maharashtra}
          {Software Engineer}{Jul 2018 \textbf{--} Oct 21, Full-time}
    
    \resumeItemListStart
        % ######### PROJECT 2 #########
        \projectOneHead
        {Reliability (\normalfont \textit{for Kotak Securities})}
        {Aug 2019 -- Oct 2021}
            % Summary
            \begin
                {itemize}[leftmargin=0in, label={-}]
                \item\small It is a banking MIS System to view the account/customer level reports.

                \item\small Comprehensively analyze and understand the Client Requirement Forms (CRFs), ensuring a clear understanding of project objectives, specifications, and client expectations.
                \item\small Implement UI and efficient Optimization, data structures, and caching mechanisms to streamline data retrieval and processing, reducing latency and improving user experience.
                % \item\small Creation of SSIS Package to upload the files from front end.
            \end{itemize}
    
            % Skills
            \begin{itemize}[leftmargin=-0.15in, label={}]
                \item\textit{\textbf{\fontsize{10}{12}\selectfont 
                    Angular 5, MS-SQL, MVC, Java, Web API, Github, SVN, Eclipse, VS Code, Postman, Git
                }}
            \end{itemize}

        % ######### PROJECT 1 #########
        \projectTwoHead
        {Customer Relationship Management (\normalfont \textit{for Kotak Securities})}
        {Sep 2018 -- Jul 2019}
            % Summary
            \begin{itemize}[leftmargin=0in, label={-}]
                \item\small It is a application handles all the service request which are raised by customers.
                \item\small Active participation in all SDLC phases for change requests, spanning from requirement gathering to  deployment.
                \item\small Create and managing schema objects and maintaining Referential Integrity.
                \item\small Created SSIS package to populate data from various data sources.
            \end{itemize}
                
    
            % Skills
            \begin{itemize}[leftmargin=-0.15in, label={}]
                \item\textit{\textbf{\fontsize{10}{12}\selectfont 
                    Angular 5, MS-SQL, MVC, Java, Web API, SSIS, SSRS, SVN, VS Code, Postman, Git
                }}
            \end{itemize}
    \resumeItemListEnd
    
    \resumeSubHeadingListEnd

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {St. John College of Engineering and Management}{Palghar}
      {Bachelors Degree in Computer Science}{Jul. 2014 -- Jul. 2018}
    \resumeSubheading
      {Ukkarsha Vidyalaya and Junior College}{Virar}
      {General Science}{Jul. 2012 -- July. 2014}
  \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  % \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        
        \textbf{Languages:}{ C, Java, JavaScript, TypeScript, SQL} \\ \vspace{3pt}
        
        \textbf{Technologies:}{ Angular, Node.js, Spring Boot, MySQL, MongoDB, Git, SVN, Docker, AWS, Kubernetes} \\ \vspace{3pt}
        
        \textbf{Methodologies:}{ Agile, Scrum, OOP, Functional Programming, DevOps, CI/CD, TDD} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd


%----------- SECTION:: AWARDS & ACHIEVEMENTS -----------
\section{Awards \& Achievements}
  % \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Pat On Back:}{ Led the inception-to-completion development of a web app using Angular and Spring Boot(Jan 2023)} \\ \vspace{3pt}

        \textbf{Team Award:}{ Completion of our Quarterly development task, delivered promptly and with precision.(Jun 2020)} \\ \vspace{3pt}
        
    }}
  \resumeSubHeadingListEnd



%----------- SECTION:: PROJECTS -----------

\section{Projects}
    \vspace{3pt}
    \resumeSubHeadingListStart
      
      \resumeProjectHeading
        {\textbf{Exam Portal} $|$ \emph{\href{https://github.com/devBhaskar98/Exam-Portal}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{
            The Angular-Spring Boot MCQ Test Platform is a web-based application designed to facilitate categorically organized multiple-choice question (MCQ) tests for users. 
            Admins can create quizzes by defining categories and populating them with questions, while users (students) can access these quizzes and attempt to solve them. 
            The application utilizes Angular for the frontend interface, Spring Boot for backend functionality, and MySQL for database management. 
            } 
          \resumeItemListEnd

        \resumeProjectHeading
        {\textbf{Automatic Image and Video Colourization using Deep Learning} $|$ \emph{\href{https://github.com/BRAiNCHiLD95/ImageColourisationDL}{\color{blue}GitHub}}}{}
          \resumeItemListStart
            \resumeItem{
            This project aims to enhance automated colourisation systems for monochrome and black and white images/videos by addressing existing challenges such as colour inconsistency, saturation issues, and inaccuracies in bright environments.
            Through advancements in deep learning architectures and image processing techniques, the objective is to develop a more efficient and accurate colourisation process, reducing the need for manual intervention and improving overall results.
            } 
          \resumeItemListEnd

          \vspace{1pt}
      
    \resumeSubHeadingListEnd

% % ----------- HOBBIES -----------

\section{Hobbies}
% \vspace{3pt}
  \resumeSubHeadingListStart
    \small{\item{Cricket, Fitness, Reading, Travelling}}
  \resumeSubHeadingListEnd


%----------- RELEVANT COURSEWORK -----------

% \section{Relevant Coursework}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \small{\item{
        % \textbf{Major coursework:}{ Materials Science, Electrical Circuits I-II, Digital System Design, Numerical Methods, Probability Theory, Electronics I-II, Signals and Systems, Electromagnetic Field Theory, Energy Conversion, System Dynamics and Control, Communication Engineering, Pattern Recognition, Introduction to Digital Signal Processing, Introduction to Digital Communications, Introduction to Database Systems, Introduction to Image Processing, Machine Vision} \\ \vspace{3pt}
        
        % \textbf{Minor coursework:}{ Discrete Computational Structures, Introduction to Object-Oriented Programming, Data Structures and Algorithms, Computer Organization, Fundamentals of Software Engineering}
    % }}
  % \resumeSubHeadingListEnd



%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
  % \resumeSubHeadingListEnd







%----------- REFERENCES -----------

% \section{References}
  % \vspace{2pt}
  % \resumeSubHeadingListStart
    % \item{References available upon request.}
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}